---
output:
  html_document: default
  pdf_document: default
---
Data Obtained from https://www.kaggle.com/datasets/kuchhbhi/cpga-iq-placement

Central Objective: determine if students with an IQ over 115 have a gpa of above 3.5
```{r}
getwd()
```
load libraries
```{r}
library(caret)
library(class)
library(ISLR)
library(e1071)
library(cluster)
```
Import .csv file
```{r}
Students <- read.csv("student_clustering.csv", header = TRUE, sep = ",")
```
Remove all missing values
```{r}
Students <- na.omit(Students)
head(Students)
```
Turn IQ>115 into new binary variable
```{r}
Students$highiq <-ifelse(Students$iq>115,1,0)
```
Find Average GPA out of dataset
```{r}
mean(Students$cgpa)
```
Turn CGPA>6.9834 into new binary variable
```{r}
Students$highcgpa <- ifelse(Students$cgpa>6.9834,1,0)
```
Summarize 
```{r}
str(Students)
```
Create Pivot Table
```{r}
table(StudentsCgpa=Students$highcgpa, StudentsIQ=Students$highiq)
```
P(IQ>115) = 43/200 students have high IQs or .215 or 21.5%

P(CGPA>6.9834) = 57/200 students have high CGPAs or .57 or 57%

P(CGPA>6.9834|IQ>115) = 43/43+57 = .43 or 43%

43% of people with an IQ higher than 115 will have a GPA higher than average





